---
title: "WORKSHEET-3A"
author: "Angel Janica Marie De Jesus"
date: "2022-10-28"
output: pdf_document
---
Worksheet-3a in R
Worksheet for R Programming
Instructions:
  •	Use RStudio or the RStudio Cloud accomplish this worksheet.
•	Save the R script as RWorksheet_lastname#3a.R.
•	On your own GitHub repository, push the R script, the Rmd file, as well as this pdf worksheet to the repo you have created before.
•	Do not forget to comment your Git repo on our VLE
•	Accomplish this worksheet by answering the questions being asked and writing the code manually.
Reminder
•	To create a chunk of codes, you need to indicate this structure

Figure 1: R Chunk
•	You can add chunk options if you want, like:
  –	echo: Whether to echo the source code in the output document (someone may not prefer reading your smart source code but only results).

Using Vectors
1. There is a built-in vector LETTERS contains the uppercase letters of the alphabet
and letters which contains the lowercase letters of the alphabet.
LETTERS
## [1] "A" "B" "C" "D" "E" "F" "G" "H" "I" "J" "K" "L" "M" "N" "O" "P" "Q" "R" "S"
## [20] "T" "U" "V" "W" "X" "Y" "Z"
letters
## [1] "a" "b" "c" "d" "e" "f" "g" "h" "i" "j" "k" "l" "m" "n" "o" "p" "q" "r" "s"
## [20] "t" "u" "v" "w" "x" "y" "z"
Based on the above vector LETTERS:
a. You need to produce a vector that contains the first 11 letters.
```{r,include=TRUE}
LETTERS [1:11]
```
b. Produce a vector that contains the odd numbered letters.
```{r,include=TRUE}
oddletters <-LETTERS[1:26 %% 2 ==1]
oddletters
```
c. Produce a vector that contains the vowels
```{r,include=TRUE}
vowels <- LETTERS [c(1,5,9,15,21)]
vowels
```

Based on the above vector letters: d. Produce a vector that contains the last 5 lowercase letters.
```{r,include=TRUE}
fiveletters <- letters[21:26]
fiveletters
```
e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
```{r,include=TRUE}
fiveletters <- letters[15:24]
fiveletters
```

2. Create a vector with the average temperatures in April for Tuguegarao City, Manila, Iloilo City, Tacloban,
Samal Island, and Davao City. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.

a. What is the R code and its result for creating a character vector for the city/town of Tuguegarao City,
Manila, Iloilo City, Tacloban, Samal Island, and Davao City? Name the object as city. The names
should follow the same order as in the instruction.
```{r, include=FALSE}
citytown <-c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", "Samal Island", "Davao City")
citytown
```

b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees. Name the object as temp.
Write the R code and its output. Numbers should also follow what is in the instruction.
```{r,include=TRUE}
temp <-c(42, 39, 34, 34, 30, 27)
temp
```

c. Associate the temperature temp with the city by using names() function. What is the R code and its
result.
```{r,include=TRUE}
names(temp) <- citytown
temp
```

d. From the answer in d, what is the content of index 5 and index 6? What is its R code?
```{r,include=TRUE}
names_index56 <- temp[5:6]
names_index56
```

Using Matrices
2. Create a matrix of one to eight and eleven to fourteen with four columns and three # rows.

a. What will be the R code for the #2 question and its result?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
tab1
```

b. Multiply the matrix by two. What is its R code and its result?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
result <- tab1 * 2
result
```

c. What is the content of row 2? What is its R code?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
tab1
```

```{r,include=TRUE}
content <- c(tab1[2,1], tab1[2,2], tab1[2,3], tab1[2,4])
content
```
d. What will be the R code if you want to display the column 3 and column 4 in row 1 and row 2? What
is its output?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
tab1
```

```{r,include=TRUE}
content <- c(tab1[1,3], tab1[1,4], tab1[2,3], tab1[2,4])
content
```
e. What is the R code is you want to display only the columns in 2 and 3, row 3? What is its output?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
tab1
```

```{r,include=TRUE}
content <- c(tab1[3,2], tab1[3,3])
content
```
f. What is the R code is you want to display only the columns 4? What is its output?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
tab1
```

```{r,include=TRUE}
content <- c(tab1[1,4], tab1[2,4], tab1[3,4])
content
```

g. Name the rows as isa, dalawa, tatlo and columns as uno, dos, tres, quatro for the matrix that was
created in b.‘. What is its R code and corresponding output?
```{r,include=TRUE}
tab1 <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
tab1
```

```{r,include=TRUE}
dimnames(tab1) <- list(c("isa", "dalawa", "tatlo"),c("uno", "dos", "tres", "quatro"))
tab1
```
h. From the original matrix you have created in a, reshape the matrix by assigning a new dimension with
dim(). New dimensions should have 2 columns and 6 rows. What will be the R code and its output?
```{r,include=TRUE}
tab1 <- matrix(1:8, 11:14, nrow = 3, ncol = 4)
```

```{r,include=TRUE}
tab1
```

```{r,include=TRUE}
newtab <- c(1,2,3,4,5,6,7,8,11,12,13,14)
newtab
```

```{r,include=TRUE}
x <- matrix(newtab, nrow = 6, ncol = 2)
x
```

```{r,include=TRUE}
dim(x)
```

Using Arrays
3. An array contains 1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1

a. Create an array for the above numeric values. Each values will
be repeated twice
What will be the R code if you are to create a three-dimensional
array with 4 columns and 2 rows. What will be its output?

```{r,include=TRUE}
a <- c(1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1)
a
```

```{r,include=TRUE}
x <- array(rep(a, 2), dim = c(2,4,3))
x
```
b. How many dimensions do your array have? # It has 3 dimensions.
c. Name the rows as lowercase letters and columns as uppercase letters starting from the A. The array
names should be “1st-Dimensional Array”, “2nd-Dimentional Array”, and “3rd-Dimensional Array”.
What will be the R codes and its output?
```{r,include=TRUE}
a <- c(1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1)
a
```

```{r,include=TRUE}
x <- array(rep(a, 2), dim = c(2,4,3))
x
```

```{r,include=TRUE}
dimnames(x) <- list( letters[1:2], LETTERS[1:4], c("1st-Dimensional Array", "2nd-Dimensional Array", "3rd-Dimentional Array"))
x
```
