---
title: "Worksheet-4"
author: "Angel Janica Marie De Jesus"
date: "2022-11-23"
output: pdf_document
---

##1. The table below shows the data about shoe size and height. Create a data frame..
##a. Describe the data.

```{r,echo=TRUE}
ShoeSize <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,
              7.5,10.5,8.5,12.0,10.5,
              13.0,11.5,8.5,5.0,10.0,
              6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)

Height <- c(66.0,68.0,64.5,65.0,70.0,
            64.0,70.0,71.0,72.0,64.0,
            74.5,67.0,71.0,71.0,77.0,72.0,
            59.0,62.0,72.0,66.0,64.0,67.0,73.0,
            69.0,72.0,70.0,69.0,70)

Gender <- c("F","F","F","F","M","F","M","F","M",
            "M","M","F","M","M","M","M","F","F",
            "M","F","M","M","M","F","M","M","M","M")

df <- data.frame(ShoeSize,Height,Gender)
df

```

##b. Find the mean of shoe size and height of the respondents.
##Copy the codes and results.

```{r,echo=TRUE}
summary(df)
mean(ShoeSize)
# SHOESIZE: Mean   : 9.411
# HEIGHT:   Mean   :68.57 
```

#c. Is there a relationship between shoe size and height? Why? : Yes there is a relationship between shoe size and height because the higher height will give a higher shoe size

##2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.

```{r,echo=TRUE}
Months <- c("March","April","January","November","January",
            "September","October","September","November","August",
            "January","November","November","February","May","August",
            "July","December","August","August","September","November","February","April")

factor_months_vector <- factor(Months)
factor_months_vector
```

#3. Then check the summary() of the months_vector and factor_months_vector. |
#Interpret the results of both vectors. Are they both equally useful in this case? : Yes both are very useful in this case because both will display different data that are relevant

```{r,echo=TRUE}
summary(Months)

summary(factor_months_vector)

```

#4. Create a vector and factor for the table below.

```{r,echo=TRUE}
factor_data<- c(1,4,3)


newdt <- factor(factor_data,levels = c("East","West","North"))

print(newdt)

```

#5. Enter the data below in Excel with file name = import_march.csv

#a. Import the excel file into the Environment Pane using read.table() function.

```{r,echo=TRUE}
getwd()

excel <- read.table("import_march.csv", header= TRUE,sep = ",")
excel
```

#b. View the dataset. Write the code and its result.

```{r,echo=TRUE}
View(excel)
```
