---
title: "Individual Project 1"
author: "Angel Janica Marie De Jesus"
date: "2022-11-30"
output: pdf_document
---
#Individual Project 1
Instructions:

#Extract from twitter using your developer's credentials. Choose any keyword you want. 
#Get 10000 observations "excluding retweets.
#Plot the time series from the date created. with legends. 
#Plot a graph (any graph you want)  based on the type of device - found in Source - that the user use. Include the legends.
#Create a wordcloud from the screenName


#install and load packages
install.packages('twitteR')
install.packages("RCurl")
install.packages("rtweet")
install.packages("tidytex")
install.packages("plotly")
install.packages("RColorBrewer")
install.packages("stringr")
install.packages("magrittr")
install.packages("tm")
install.packages("wordcloud")
install.packages("wordcloud2")


library("twitteR")
library("RCurl")
library(tidytex)
library(rtweet)
library(ggplot2)
library(RColorBrewer)
library(tm)
library(dplyr)
library(wordcloud)
library(wordcloud2)
library(stringr)

#install.packages("syuzhet") #for sentiment analysis
install.packages("syuzhet")
library(syuzhet)

install.packages("rdfp")
library("rdfp")
library(magrittr)

```{r, echo=TRUE}
#declare tokens and keys

CONSUMER_KEY <- "rNOC9AXlOmMwltDU6fxZGJvoc"
CONSUMER_SECRET <- "LMC48sUCCPib785PAYb1pzwjDiWueoJZthbpdpxiYUh2gxa4on"
ACCESS_TOKEN <- "1596020398365151234-Ttupby9xwEH2IPfF2aIs1SdiXHtPgo"
ACCESS_SECRET <- "yBeaMXTih50GXUOhiZBF2o2xHNuqUA9w3cUCFS0Oqt0U6"

```

```{r, echo=TRUE}
#Connect to twitter app
library(twitteR)
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)

```

```{r, echo=TRUE}

#extract 10k tweets exclude retweets #Netflix

searchTwt <- searchTwitter("#Wednesday -filter:retweets",
                           n = 10000,
                           lang = "en",
                           since = "2022-11-24",
                           until = "2022-11-30",
                           retryOnRateLimit = 120)
```

```{r, echo=TRUE}
#converet to dataframe
library("dplyr")
TwtDF <- twListToDF(searchTwt)
class(TwtDF)
names(TwtDF)
View(TwtDF)[1:5]
head(TwtDF$text)[1:5]

save(TwtDF,file = "WedTwtDF.Rdata")

#load dataset
load(file = "WedTwtDF.Rdata")
```


```{r, echo=TRUE}
#subsetting using the dplyr(package)
install.packages("dplyr")
library(dplyr)
tweetsDF <-TwtDF %>%
  select(screenName,text,created,statusSource)
```


```{r, echo=TRUE}

#group the date created
tweetsDF %>%
group_by(1) %>%
summarise(max(created), min = min(created))

tweetsDF %>% pull(created) %>% min()

tweetsDF %>% pull(created) %>% max()
```

```{r, echo=TRUE}
# creating histogram with legend
library(ggplot2)
ggplot(data = tweetsDF, aes(x = created)) +
  geom_histogram(aes(fill = ..count..)) +
  xlab("Date") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "blue", high = "red")
theme(legend.position = "topleft")

```

```{r, echo=TRUE}


# creating a wordcloud
library(dplyr)
tweet_appScreen <- tweetsDF %>% 
  select(screenName) %>%
  group_by(screenName) %>%
  summarize(count=n()) %>%
  arrange(desc(count))
```

```{r, echo=TRUE}

#convert to Corpus
library(tm)
namesCorpus <- Corpus(VectorSource(tweetsDF$screenName))
class(tweetsDF$screenName)

class(VectorSource(tweetsDF$screenName))
str(namesCorpus)

class(namesCorpus)
namesCorpus
```

```{r, echo=TRUE}

library(wordcloud)
pal <- brewer.pal(8, "Dark2")
pal <- pal[-(1:4)]
set.seed(123)

par(mar = c(0,0,0,0), mfrow = c(1,1))

wordcloud(words = namesCorpus, scale=c(3,0.5),
          max.words=500,
          random.order=FALSE,
          rot.per=0.5,
          use.r.layout=TRUE,
          colors=pal)

set.seed(1234)

wordcloud(words = tweet_appScreen$screenName,
          freq = tweet_appScreen$count,min.freq = 1,
          max.words=1000, random.order=FALSE, rot.per=0.35,
          colors = brewer.pal(8,"Dark2"))


```

```{r, echo=TRUE}

library(wordcloud2)
wordcloud2(data=tweet_appScreen, 
           size=0.8, 
           color='random-dark',
           shape = 'pentagon')

```