---
title: "Worksheet - 3b"
author: "Angel Janica Marie De Jesus"
date: "2022-11-11"
output:
  pdf_document: default
  html_document: default
---

##1. A.Write the codes.
```{r, echo=TRUE}
Respondents <- c(seq(1,20))
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
FathersOccupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
PersonsAtHome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
SiblingsAtSchool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
TypesOfHouses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)

df <- data.frame(Respondents, Sex, FathersOccupation, PersonsAtHome, SiblingsAtSchool, TypesOfHouses)

print (df)
names(df)
```

##B. Describe the data:
##The data given are the respondents information according to sex, parent occupation, people at home, siblings at school and the type of houses.

##Get the structure or the summary of the data
```{r, echo=TRUE}
summary(df)

```
##C. Is the mean number of siblings attending is 5?
```{r, echo=TRUE}
mean(SiblingsAtSchool)
##No
```


##d. Extract the 1st two rows and then all the columns using the subsetting functions. Write the codes and its output.

```{r, echo=TRUE}

sbst1 <- df[c(1,2),c(1:6)]
sbst1
```

##e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r, echo=TRUE}
sbst2 <- df[c(3,5),c(2,4)]
sbst2
```

##f. Select the variable types of houses then store the vector that results as types_houses. Write the codes.
```{r, echo=TRUE}

types_houses <- (df$'Types Of Houses')
types_houses
```
##g. Select only all Males respondent that their father occupation was farmer. Write the codes and its output.

```{r, echo=TRUE}

Male <- subset(df,Sex == '1' & FathersOccupation == '1')
Male

MaleFarm <- Male[c(2:3)]
MaleFarm
```
##h. Select only all females respondent that have greater than or equal to 5 number of siblings attending school. Write the codes and its outputs.

```{r, echo=TRUE}

Female <- subset(df,Sex == '2' & SiblingsAtSchool >= '5')
Female

FemaleSib <- Female[c(2,5)]
FemaleSib
```

##2. Write a R program to create an empty data frame. Using the following codes:
```{r, echo=TRUE}

df = data.frame(Ints=integer(),
                Doubles=double(), Characters=character(),
                Logicals=logical(),
                Factors=factor(),
                stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```
##a. Describe the results : data frame has 5 variables which are the Ints,Doubles,Characters,Logical and Factors. But the result on the tables has no data available since there is no inputted data on each variable.

##3.Interpret the graph: The graph is titled as Figure 1: Sentiments of Tweets per day - Donald trump. The x = Day of Date / Sentiments consisting of dates from July 14, 15, 17,18, 20, 21, 2020. The y = Count of Sheet1 from 0 to 4000. The graph used is a bar graph consisting of 3 sentiments(Negative, Neutral and Positive).A legend is placed at the upper right corner indicating specific colors of every sentiments such as Negative = Red, Neutral= yellow and positive = blue.